\Rpackage{MSnID} Package for Handling MS/MS Identifications

### 2014-04-01 inst/doc/msnid_vignette.Rnw
adding inst/doc directory with vignette

%\VignetteIndexEntry{MSnID Package for Handling MS/MS Identifications}
% \VignetteDepends{BiocStyle, msmsTests}
%\VignetteKeywords{Documentation}
%\VignettePackage{MSnID}
\documentclass[11pt]{article}

@@

\subsection{Downloading example mzIdentML files}
As an example we will use datasets from C.elegans proteomics study describing the effect of daf-16 mutation on the protein abundances \cite{Depuydt2013,Depuydt2014}. There will be 5 datasets corresponding to long-living glp-4; daf-2 strain and 5 datasets corresponding to the strain with compensatory mutation in daf-16 transcription factor that restores (shortens) life-span back to normal. Files available at PeptideAtlas repository \href{https://db.systemsbiology.net/sbeams/cgi/PeptideAtlas/PASS_View?identifier=PASS00308}{PASS00308}.
<<>>=
try(setInternet2(FALSE),silent=TRUE)
ftp <- "ftp://PASS00308:PJ5348t@ftp.peptideatlas.org/"
meta <- read.delim(sprintf("%sSample_Metadata.txt", ftp), as.is=T)
meta <- subset(meta, Age == 'young' & Diet == 'ff') # explore the effect of daf-16.
#for( dataset in meta$PNNL.Dataset.Name){
#   cel.path <- sprintf("%s/MSGFPlus_Results/MZID_Files/%s_msgfplus.mzid.gz", 
#                       ftp, dataset)
#   download.file(cel.path, sprintf("%s_msgfplus.mzid.gz", dataset))
#}
@

>>>>

%\VignetteIndexEntry{MSnID Package for Handling MS/MS Identifications}
%\VignetteDepends{BiocStyle, msmsTests, ggplot2}
%\VignetteKeywords{Documentation}
%\VignettePackage{MSnID}
\documentclass[11pt]{article}

@@

\subsection{Downloading example mzIdentML files}
As an example we will use datasets from C.elegans proteomics study describing the effect of daf-16 mutation on the protein abundances \cite{Depuydt2013,Depuydt2014}. There will be 5 datasets corresponding to long-living glp-4; daf-2 strain and 5 datasets corresponding to the strain with compensatory mutation in daf-16 transcription factor that restores (shortens) life-span back to normal. Files available at PeptideAtlas repository \href{https://db.systemsbiology.net/sbeams/cgi/PeptideAtlas/PASS_View?identifier=PASS00308}{PASS00308}.
<<>>=
try(setInternet2(FALSE),silent=TRUE)
ftp <- "ftp://PASS00308:PJ5348t@ftp.peptideatlas.org/"
meta <- read.delim(sprintf("%sSample_Metadata.txt", ftp), as.is=TRUE)
meta <- subset(meta, Age == 'young' & Diet == 'ff') # explore the effect of daf-16.
for( dataset in meta$PNNL.Dataset.Name){
   cel.path <- sprintf("%s/MSGFPlus_Results/MZID_Files/%s_msgfplus.mzid.gz", 
                       ftp, dataset)
   download.file(cel.path, sprintf("%s_msgfplus.mzid.gz", dataset))
}
@
